Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-12 Arxiv/main.tex
Update Arxiv/main.tex

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}},
\end{equation*}
where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.

After post-processing, Laplace noise is discretized. Then the accuracy bound for Laplace mechanism is obtained by:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t-1 \leq Y < t] 
= \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
\]

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism. By applying the accuracy bound into Hellinger distance in our case:
$$
\begin{array}{rcl}
& Pr\big[\hlg(\bysinfer(\dataobs), r_L ) 
= \hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
\end{array}
$$
where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
By simplification the Hellinger distance in $\hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:

@@

  \item[\textbf{case 2:}] \textbf{t is odd}\\
  let $t = 2 m + \frac{1}{2}$
  \begin{align*}
   Pr\Bigg[ \hlg(\bysinfer(\dataobs), r_L ) = & \\
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \cdot \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
  \end{align*}

@@

\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $2$.
\[
Pr[\lfloor Y \rfloor = t] = Pr[ t-1 \leq Y < t] = \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{2}} - e^{- \frac{\epsilon (t)}{2}}).
\]

>>>>

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function\cite{dwork2014algorithmic}:
$$
Pr[|Y| \geq t \cdot b] = e^{- t},
$$
where $Y \thicksim Lap(b)$, i.e.,
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}
\end{equation*}
in our case, where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.

After post-processing, Laplace noise is discretized. Then the probability mess function for discretized Laplace mechanism is obtained by:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t-1 \leq Y < t] 
= \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
\]

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism. By applying the probability mess function of discretized Laplace mechanism in our case with Hellinger distance, we get:
$$
\begin{array}{rcl}
& Pr\big[\hlg(\bysinfer(\dataobs), r_L ) 
= \hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
\end{array}
$$
where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
By simplification the Hellinger distance in $\hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:

@@

  \item[\textbf{case 2:}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
   Pr\Bigg[ \hlg(\bysinfer(\dataobs), r_L ) = & \\
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \cdot \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
  \end{align*}

@@

\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $2$.
